% Resume

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Harsh Krishna} % Your name
\address{+91 84477 60367 \\ New Delhi, India} 
\address{\href{mailto:harsh.krishna2016@gmail.com}{harsh.krishna2016@gmail.com} \\ \href{https://linkedin.com/in/harsh-krishna-5b6664219}{Linkedin} \\ \href{https://harshkrishna17.github.io/}{Portfolio}} 

\begin{document}

% Education

\begin{rSection}{Education}

{\bf Humanities}, Sardar Patel Vidyalaya \hfill {June 2022}\\
Percentage: 96\%

\end{rSection}

% Skills and Strengths	

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & R, Python \\
Frameworks & ShinyR, ggplot2, tidyverse, dplyr, devtools, pandas, numpy, matplotlib \\
Tools & Microsoft Excel, Tableau Public, Git \\
Languages & English, Hindi, Tamil \\
\end{tabular}\\

\end{rSection}

% Projects

\begin{rSection}{PROJECTS}

\item \textbf{ggshakeR} {\emph{Author; R, Markdown} [Oct 2021 - Present]} \hfill \href{https://github.com/abhiamishra/ggshakeR}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item One of the authors of R’s \textbf{1st} all-in-one visualization and analysis package for openly available soccer data.
     \item Authored \textbf{5} functions and contributed additional features to an extra \textbf{3} functions while working with other contributors as an open source project. Functions are compatible with \textbf{JSON data and specific APIs} while also supporting the use of \textbf{web scraped data}.
    \item Helped create an official landing page with GitHub Pages that experiences an average of \textbf{800+} views and \textbf{100+} unique visitors per week. Initial release and updates invite upwards of \textbf{1000+} views on the package.
    \item Created the \textbf{ggshakeR library}, a secondary website with articles and a helper code base pertaining to the usage of R in sports analytics.
    \item Recognized by various open source projects and package aggregators such as \textbf{PySport} and \textbf{LibHunt} while being one of the \textbf{most in-demand packages} in the soccer analytics community.
 \end{itemize}
\item \textbf{Player Finishing Overview} {\emph{Creator; R, ShinyR, ggplot2} [Apr 2022]} \hfill \href{https://github.com/harshkrishna17/PlayerFinishingOverviewShiny}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Interactive web app using \textbf{ShinyR} that generates a dashboard of visualizations that can be useful in getting an overview of a soccer player’s finishing ability.
     \item Allows users to set several parameters to their choosing and download the plot subsequently created.
     \item Deployed using shinyapps.io on free tier. 
 \end{itemize}
 
\end{rSection} 

% Achievements 

\begin{rSection}{Achievements} 

\begin{itemize}
    \item \textbf{Trinity College London:} Attempted practical and theory exams for electronic keyboard up till grade 3, achieving a grade of distinction consistently.
\end{itemize}

\end{rSection}
\end{document}
